---
title: "Reformat main data"
author: "Collin Reinking"
date: "August 4, 2018"
output: html_document
---

```{r}
library(tidyverse)
library(rio)
library(here)
library(janitor)
library(data.table)
```

I want to create a data.frame of the original names and what I will be changing them to so that I can change them back when I output.  This way I don't have to change any names in Tableau.
```{r create data.frame of name changes}
df.raw.head <- import(here('W209 Data - 20180725.csv'), nrows = 10)
lookup_names <- data.frame(t_names = names(df.raw.head), r_names = names(df.raw.head %>% clean_names('upper_camel')), stringsAsFactors = FALSE)
remove(df.raw.head)
lookup_names
```

```{r}
df.raw <- import(here('W209 Data - 20180725.csv')) %>% 
  clean_names('upper_camel') %>% 
  print()
```

```{r}
lookup_program_title <- import(here('program_title_mapping_updated.csv')) %>% 
  rename(ProgramName = program_name,
         ProgramTitle = fake_title) %>% 
  select(ProgramName,ProgramTitle) %>% 
  print()
```
```{r}
df.raw %>% 
  anti_join(lookup_program_title, by='ProgramName') %>% 
  distinct(ProgramName) %>% 
  #export("ProgramsWithNoReplacementName.csv")
  print()
  
```

```{r}
df.uncorrected <- df.raw %>% 
  inner_join(lookup_program_title, by='ProgramName') %>% 
  select(-ProgramName) %>% 
  select(-CountySize) %>%
  select(-ProgramType) %>% 
  select(-DetailProgramType) %>%
  select(-GeographicTerritory) %>% 
  select(-Network) %>% 
  select(-NetworkType) %>% 
  
  mutate(Education = str_extract(Education, ".+?(?= \\()")) %>% #only keep characters up until first occurance of " ("
  mutate(ViewDate = as.Date(ViewDate,'%Y-%m-%d'),
         BroadcastDate = as.Date(BroadcastDate, '%Y-%m-%d')
  ) %>% 
  filter(ViewDate >= BroadcastDate) %>% 
  print()
```

```{r}
str(df.uncorrected)
```

```{r}
df <- df.uncorrected %>% 
  group_by(Id,Gender, Age, HouseholdIncome, Education,Occupation,
           ProgramTitle, EpisodeName, BroadcastDate,ProgramDuration) %>% 
  summarize(ViewingMins = sum(ViewingMins),
         ViewDate = max(ViewDate)) %>% 
  mutate(Delaydays = as.integer(ViewDate - BroadcastDate)) %>% 
  ungroup() %>% 
  print()
```

```{r}
id_lists <- df %>% 
  select(ProgramTitle, Id) %>% 
  group_by(ProgramTitle) %>% 
  summarize(AllProgramIds = list(unique(Id)), NId = n_distinct(Id)) %>%
  arrange(-NId) %>%
  mutate(CumulativePercentile = cumsum(NId)/sum(NId)) %>% 
  print()
```


```{r}
id_lists %>% 
  mutate(Rank = row_number()) %>% 
  ggplot(aes(x=Rank, y=CumulativePercentile,color = CumulativePercentile<.9)) +
  geom_point()


id_lists %>% 
  filter(CumulativePercentile>=.8)
```

```{r}
df.reduced <- df %>%
  semi_join(id_lists %>% filter(CumulativePercentile<=.8),
            by = "ProgramTitle") %>% 
  mutate(ViewingMins = if_else(ViewingMins>ProgramDuration, ProgramDuration,ViewingMins)) %>% 
  print()
  
  
  
```


```{r}
investigate <- df.reduced %>% 
  group_by(ProgramTitle, EpisodeName, Id, BroadcastDate, ViewDate) %>% 
  mutate(n = n()) %>% 
  ungroup() %>% 
  filter(n>1)
```

```{r}
investigate %>% 
  arrange(-n,Id, ProgramTitle, EpisodeName, BroadcastDate, ViewDate) %>% 
  select(Id, everything()) %>% 
  #export(here("wtfIsGoingOnHere.csv"))
  print()
```

I will correct the issue of mutltiple durations of the same program,episode, view, BroadcastDate, by selecting only the one with the highest duration and summing the max viewed minutes
```{r}
investigate %>% 
  group_by_at(vars(-c(ViewingMins,ProgramDuration))) %>% 
  summarize(ProgramDuration = max(ProgramDuration),
            ViewingMins = max(ViewingMins))
```

df.reduced : 4,936,030 rows
investigate : 77,773 rows 
indestigate reduced: 38,073
reduced by: 39,700


```{r}
df.reduced.corrected <- df.reduced  %>% 
  group_by_at(vars(-c(ViewingMins,ProgramDuration))) %>% 
  summarize(ProgramDuration = max(ProgramDuration),
            ViewingMins = max(ViewingMins)) %>% 
  ungroup() %>% 
  print()
```

```{r}
df.reduced.corrected %>% 
  skimr::skim()
```


```{r}
bin = case_when(Age <= 20 ~ '20',
                Age <= 23 ~ '23',
                Age <= 26 ~ '26',
                Age <= 29 ~ '29',
                Age <= 32 ~ '32',
                Age <= 35 ~ '35',
                Age <= 38 ~ '38',
                Age <= 41 ~ '41',
                Age <= 44 ~ '44',
                Age <= 47 ~ '47',
                Age <= 50 ~ '50')
```



```{r}
rename_fun <- function(dat){
  old_names <- data.frame(r_names = names(dat), stringsAsFactors = FALSE)
  
  new_names <- old_names %>% 
    left_join(lookup_names, by = 'r_names' ) %>% 
    mutate(final_names = coalesce(t_names, r_names)) %>% 
    pull(final_names)
  
  
  stats::setNames(dat, new_names)
}



df.final <- df.reduced.corrected %>% 
  #filter(as.Date(ViewDate,'%m/%d/%Y') >= as.Date(BroadcastDate, '%m/%d/%Y') ) %>% 
  
  mutate(FemaleId = if_else(Gender == "F", Id, 'MALE'))%>% 
  mutate(MaleId = if_else(Gender == "M", Id, 'FEMALE'))%>% 
  mutate(bin = case_when(Age <= 20 ~ '20',
                Age <= 23 ~ '23',
                Age <= 26 ~ '26',
                Age <= 29 ~ '29',
                Age <= 32 ~ '32',
                Age <= 35 ~ '35',
                Age <= 38 ~ '38',
                Age <= 41 ~ '41',
                Age <= 44 ~ '44',
                Age <= 47 ~ '47',
                Age <= 50 ~ '50')) %>% 
  group_by(ProgramTitle,bin) %>% 
  mutate(pb_n_females = n_distinct(FemaleId)-1,
         pb_n_males = n_distinct(MaleId)-1) %>% 
  ungroup() %>% 
  group_by(ProgramTitle) %>%
  mutate(p_max_b_n_female = max(pb_n_females),
         p_max_b_n_male = max(pb_n_males)) %>% 
  mutate(GenderMaxLine = max(p_max_b_n_female, p_max_b_n_male)) %>% 
  ungroup() %>% 
  mutate(`Perc Viewed` = ViewingMins/ProgramDuration) %>% 
  rename_fun() %>% 
  print()
  
```
```{r}
export(df.final %>% 
         select(-bin) %>% 
         select(-pb_n_females) %>%  
         select(-pb_n_males) %>%  
         select(-p_max_b_n_female) %>%  
         select(-p_max_b_n_male),
       'CorrectedDataSet_2018_08_05.csv')
```



# Create Also Viewed Table

```{r create a list of unique user IDs for each program}
id_lists <- df.reduced.corrected %>% 
  select(ProgramTitle, Id) %>% 
  group_by(ProgramTitle) %>% 
  summarize(AllProgramIds = list(unique(Id)), NId = n_distinct(Id)) %>%
  arrange(-NId) %>% 
  print()

```


```{r count the number of shared IDs between each pair of programs}
n <- dim(id_lists)[1]**2
dt <- data.table(pa=rep(NA,n), pb=rep(NA,n), shared_id_count=rep(-1,n) ) #the -2 is for validation later
dt.mat <- as.matrix(dt)

#this is going to take a while
#doing this with a loop is lame but...
i <- 0
for(row_a in 1:nrow(id_lists)){
  for(row_b in 1:nrow(id_lists)){
    i <- i+1
    dt.mat[[i,'pa']] = id_lists[[row_a, "ProgramTitle"]]
    dt.mat[i,'pb'] = id_lists[[row_b, "ProgramTitle"]]
    dt.mat[[i,'shared_id_count']] = length(
      intersect(
        id_lists[[row_a,'AllProgramIds']],
        id_lists[[row_b,'AllProgramIds']]
      )
    )
  }
}
```


```{r convert to data.frame}
shared_viewer_counts <- as.data.frame(dt.mat, stringsAsFactors = FALSE) %>% 
  mutate(shared_id_count = as.integer(shared_id_count))
```

```{r remove irrelevant row}
shared_viewer_counts <- shared_viewer_counts %>% 
  filter(shared_id_count>0) %>% 
  print()
```

```{r rename columns and export}
shared_viewer_counts %>% 
  arrange(-shared_id_count) %>% 
  filter(pa != pb) %>% 
  rename(`Program Title` = pa,
         `Viewers Also Watched` = pb,
         `Number of Viewers` = shared_id_count) %>% 
  mutate(sort_order = row_number()) %>% 
  export(here('shared_viewer_counts.csv'))
```

```{r}
df.reduced.corrected %>% 
  count(Id)
```

